### 2022-12-06 rough_analysis.Rmd
Basic visuals and analysis for A1

For the first dataset, we are looking at houses are are only within the [NAmes, Edwards, BrkSide neighborhoods] and are looking at how

SalePrice ~ SqFt (GrLIvArea)

and if SalesPrice depends on neighborhood.

```{r echo=FALSE}
library(tidyverse)
library(plotly)

housing = read.csv(file = "train.csv")
a1_set = housing %>% select(SalePrice, Neighborhood, GrLivArea) %>% filter( Neighborhood == c("NAmes", "Edwards", "BrkSide"))
```

Initializing any required packages and calling in the data with some light filtering, we can take a look at the dataset and visualize what the datalooks like with some cursory visuals.

```{r}

a1_set %>% ggplot(aes(x = (GrLivArea), y = SalePrice/1000, color = Neighborhood)) + geom_point() + stat_smooth(method = "lm")

a1_set %>% ggplot(aes(x = SalePrice/10000, fill = Neighborhood)) + geom_histogram(bins =20)
```

We can see in the dataset that there is a difference in slope/intercept values per group

```{r}
#drive home a comparision in means to signify a difference in mean values.
n_means <- aov(SalePrice ~ Neighborhood, data = a1_set)
mean_diff <- TukeyHSD(n_means, conf.level = 0.95)
mean_diff
fit <- lm(SalePrice ~ Neighborhood, data = a1_set)
```

### 2022-12-06 rough_analysis.Rmd
small typos, needs relook

@@
 mean_diff
-fit <- lm(SalePrice ~ Neighborhood, data = a1_set)
+fit <- lm(SalePrice ~ GrLivArea + Neighborhood + GrLivArea*Neighborhood, data = a1_set)
 ```

### 2022-12-06 StatsProject_draft_Caro.Rmd
Update Carolina branch with StatsProject_draft_Caro.Rmd

---
title: "Statistics Project"
output: html_notebook
---

# ANALYSIS 1

Goal: Estimate how SalesPrice of the house is related to the square footage of the living area of the house & if SalesPrice (and its relationship to square footage) depends on which neighborhood the house is located in. We are only interested at looking at houses in the NAmes, Edwards & BrkSide neighborhoods.

## Packages
```{r}
library(dplyr)
library(readr)
library(tidyverse)
```

## Read in data
```{r}
train <- read.csv("train.csv")
test <- read.csv("test.csv")

head(train)
head(test)
```
## Filter data on neighborhoods 
```{r}
train_a1 <- dplyr::filter(train,Neighborhood =="Edwards" | Neighborhood =="NAmes" | Neighborhood == "BrkSide")
test_a1 <- dplyr::filter(test,Neighborhood =="Edwards" | Neighborhood =="NAmes" | Neighborhood == "BrkSide")

head(train_a1)
head(test_a1)
```
## Summary Statistics
```{r}
summary(train_a1)
summary(test_a1)
```
## EDA 
```{r}
train_a1 %>% ggplot(aes(x = (GrLivArea), y = SalePrice/1000, color = Neighborhood)) + geom_point() + stat_smooth(method = "lm")

train_a1 %>% ggplot(aes(x = SalePrice/10000, fill = Neighborhood)) + geom_histogram(bins =20)

train_a1 %>% ggplot(aes(x = GrLivArea, fill = Neighborhood)) + geom_histogram(bins =20)
```
## Log Transforms 
```{r}
# histograms with log transform on each individual variables
train_a1 %>% ggplot(aes(x = log(SalePrice/10000), fill = Neighborhood)) + geom_histogram(bins =20)

train_a1 %>% ggplot(aes(x = log(GrLivArea), fill = Neighborhood)) + geom_histogram(bins =20)

train_a1 %>% ggplot(aes(x = log(GrLivArea), y = SalePrice/1000, color = Neighborhood)) + geom_point() + stat_smooth(method = "lm")

train_a1 %>% ggplot(aes(x = (GrLivArea), y = log(SalePrice/1000), color = Neighborhood)) + geom_point() + stat_smooth(method = "lm")

train_a1 %>% ggplot(aes(x = log(GrLivArea), y = log(SalePrice/1000), color = Neighborhood)) + geom_point() + stat_smooth(method = "lm")
```

# Linear Model
```{r}
fit <- lm(log(SalePrice) ~ log(GrLivArea) + Neighborhood + GrLivArea*Neighborhood, data = train_a1)
summary(fit)
confint(fit)

plot(fit)
```
# ANOVA 
```{r}
res.aov <- aov(log(SalePrice)~log(GrLivArea)+Neighborhood+Neighborhood*GrLivArea, data = train_a1)
summary(res.aov)
```
```{r}
library(car)
# QQPlot
qqPlot(log(train_a1$SalePrice))

# histogram of residuals 
h <- hist(fit$residuals, breaks = 10, density = 10,col = "lightgray",main = "Residuals") 
xfit <- seq(min(fit$residuals), max(fit$residuals), length = 40) 
yfit <- dnorm(xfit, mean = mean(fit$residuals), sd = sd(fit$residuals)) 
yfit <- yfit * diff(h$mids[1:2]) * length(fit$residuals) 
```

### 2022-12-10 rough_analysis.Rmd
small typos, needs relook
Rough Completion of FS/ BE/ SW model generation

@@
 
-SalePrice ~ SqFt (GrLIvArea)
+SalePrice ~ SqFt (GrLIvArea) + Neighborhood
 
@@
 library(plotly)
+library(car)
 
 housing = read.csv(file = "train.csv")
+numeric_housing = housing %>% select_if(is.numeric)
 a1_set = housing %>% select(SalePrice, Neighborhood, GrLivArea) %>% filter( Neighborhood == c("NAmes", "Edwards", "BrkSide"))
@@
 ```{r}
-#drive home a comparision in means to signify a difference in mean values.
+#Comparison of Means/Coefficients to signify a difference in sample groups from different neighborhoods.
 n_means <- aov(SalePrice ~ Neighborhood, data = a1_set)
@@
 ```
+
+Analysis 2:
+
+Rough approach to Forwards Selection / Backwards Elimination / Stepwise Selection model generation:
+
+```{r}
+
+library(caret)
+train.control = trainControl(method = "cv", number = 10)
+step.model = train(SalePrice ~.-GarageArea, data = housing %>% select_if(is.numeric) %>% drop_na(), method = "leapBackward", trControl = train.control)
+step.model$modelInfo
+```
+
+For the process of forward feature selection or backwards feature elimination, we can use the olsrr package to do most of the calculations for us. This can be seen as follows:
+
+```{r}
+#install.packages("olsrr")
+library(olsrr)
+
+#turning all character columns into factors for LR: 
+character_names = housing %>% select_if(is.character) %>% names()
+housing[character_names] = lapply(housing[character_names], factor)
+
+fit_numeric = lm(SalePrice ~., data = housing %>% select_if(is.numeric))
+
+#forwards selection: 
+forward = ols_step_forward_p(fit_numeric, penter = 0.05, details = FALSE)
+
+backwards = ols_step_backward_p(fit_numeric, prem = 0.05, details = FALSE)
+
+stepwise = ols_step_both_p(fit_numeric, pent = 0.05, prem =0.05, details = FALSE)
+```
+
+```{r}
+for(i in housing %>% names()){
+  print(nlevels(housing %>% select(i)))
+}
+
+lapply(housing[character_names], nlevels)
+```

### 2022-12-10 rough_analysis.Rmd
Dialouge for document + Additional model components for A2

@@
-For the first dataset, we are looking at houses are are only within the [NAmes, Edwards, BrkSide neighborhoods] and are looking at how
+For the first analysis, we are looking at houses are are only within the locale of [NAmes, Edwards, BrkSide neighborhoods] and at how Sale Price can possibly change
+with respect to the Size of the living area and the Neighborhood in which the property is located, which can be visualized with the equation:
 
-SalePrice ~ SqFt (GrLIvArea) + Neighborhood
+SalePrice ~ SqFt (GrLIvArea) + Neighborhood + GrLIvArea:Neighborhood
 
-and if SalesPrice depends on neighborhood.
+Pulling the data into R and performing some rudimentary cleaning;
 
-```{r echo=FALSE}
+```{r include=FALSE}
 library(tidyverse)
@@
 library(car)
+library(caret)
+library(olsrr)
+```
 
+```{r RMSE function}
+ModelRMSE <- function(res){
+  retRMSE <- sqrt(mean(res^2))
+  return(retRMSE)
+}
+```
+
+```{r CVPress function}
+CVPress <- function(input_model){
+  pred_res = resid(input_model)/(1 - lm.influence(input_model)$hat)
+  press <- sum(pred_res^2)
+  return(press)
+}
+```
+
+```{r}
 housing = read.csv(file = "train.csv")
+test_housing = read.csv(file = "test.csv")
+
 numeric_housing = housing %>% select_if(is.numeric)
@@
 
-Initializing any required packages and calling in the data with some light filtering, we can take a look at the dataset and visualize what the datalooks like with some cursory visuals.
+We can take a look at the dataset and visualize what the datalooks like with some cursory visuals.
+During this step, we want to analyze any heavy correlation that the dataset might have, and account for it in any of our developing models;
 
@@
 
-We can see in the dataset that there is a difference in slope/intercept values per group
+From visual inspection, we can identify that there is a visual difference in slope/intercept values per group, and can use methods to identify and quantify what these values are.
 
@@
 #Comparison of Means/Coefficients to signify a difference in sample groups from different neighborhoods.
+### comparison of means for the groups
 n_means <- aov(SalePrice ~ Neighborhood, data = a1_set)
@@
 mean_diff
-fit <- lm(SalePrice ~ GrLivArea + Neighborhood + GrLivArea*Neighborhood, data = a1_set)
+
+### linear model with interactions explained per group
+fit <- lm(SalePrice ~ log(GrLivArea) + Neighborhood + GrLivArea*Neighborhood, data = a1_set)
+summary(fit)
+
+#RMSE: 
+ModelRMSE(fit$residuals)
 ```
@@
 
+For Analysis 2, we need to generate 4 models using variations of parameters selected by Forwards Parameter Selection, Backwards Elimination, Stepwise Selection, and a 
+personalized custom approach.
+
+Using these paramters, we can generate Adjusted R^2 values, CV Press statistics, and finally submit our model to the Kaggle website to obtain a "Kaggle Score" for each model.
+
+This process begins as follows:
+
 Rough approach to Forwards Selection / Backwards Elimination / Stepwise Selection model generation:
@@
 ```{r}
-
-library(caret)
-train.control = trainControl(method = "cv", number = 10)
-step.model = train(SalePrice ~.-GarageArea, data = housing %>% select_if(is.numeric) %>% drop_na(), method = "leapBackward", trControl = train.control)
-step.model$modelInfo
+#bad approach, maybe, I can't get it to work 
+#train.control = trainControl(method = "cv", number = 10)
+#step.model = train(SalePrice ~.-GarageArea, data = housing %>% select_if(is.numeric) %>% drop_na(), method = "leapBackward", trControl = train.control)
+#step.model$modelInfo
 ```
 
-For the process of forward feature selection or backwards feature elimination, we can use the olsrr package to do most of the calculations for us. This can be seen as follows:
+For the process of forward feature selection or backwards feature elimination, we can use the `olsrr` package to do most of the selection work for us. This can be seen as follows:
 
@@
 #install.packages("olsrr")
-library(olsrr)
 
@@
 
-fit_numeric = lm(SalePrice ~., data = housing %>% select_if(is.numeric))
+fit_numeric = lm(SalePrice ~., data = housing %>% select_if(is.numeric)) # does not account for categorical parameters !!!
 
@@
 
+From these methods we can pull our the corresponding models and analyze the statistics as well as the parameters that we chosen, to verify that first, there was a reduction in selection in the parameters for the LM and second,
+
+This step might not be necessary but could improve the quality of the model. Analysis shows a marginal improvement to R^2 and marginal deteriorate to PRESS Stat when rm'ing outliers.
+
+Outlier ID# : 692, 1183,  Excessively Expensive > 700k
+Outlier ID# : 314, 336, 256, 707    Excessively Large > 100k sqr ft.
+
 ```{r}
-for(i in housing %>% names()){
-  print(nlevels(housing %>% select(i)))
-}
+#I'm not sure if this is the best way to do it, but it highlights the requirement of the transform
 
-lapply(housing[character_names], nlevels)
+boxplot(numeric_housing) #<-visualize outliers
+
+#filtered_nh = numeric_housing[-c(692, 1183, 314, 336, 256, 707), ] #filters out outliers 
+#filtered_nh$SalePrice = log(filtered_nh$SalePrice) 
+#filtered_nh$LotArea = log(filtered_nh$LotArea)
+
+transformed_numeric = numeric_housing
+transformed_numeric$SalePrice = log(transformed_numeric$SalePrice)
+transformed_numeric$LotArea = log(transformed_numeric$LotArea)
+
+boxplot(transformed_numeric)
+
+transformed_fit = lm(SalePrice ~., data = transformed_numeric)
+
+transForward = ols_step_forward_p(transformed_fit, penter = 0.05, details = FALSE)
+
+ModelRMSE(transForward$model$residuals) #see defined functions at top of document
+CVPress(transForward$model)
+
+#boxplot(filtered_nh)
+
+#filtered_fit_numeric = lm(SalePrice ~., data = filtered_nh)                               #outlier filtered approach
+
+#f_forward = ols_step_forward_p(filtered_fit_numeric, penter = 0.05, details = FALSE)
+
+#ModelRMSE(f_forward$model$residuals) #see defined functions at top of document
+#CVPress(f_forward$model)
 ```

### 2022-12-10 rough_analysis.Rmd
Updated selection models, may have accounted for colinearity in aggressive/unintended manner. Doublecheck!

@@
 library(olsrr)
+library(corrplot)
 ```
+
+Defining functions for future use, I didn't know where to put this:
 
@@
 
-For Analysis 2, we need to generate 4 models using variations of parameters selected by Forwards Parameter Selection, Backwards Elimination, Stepwise Selection, and a 
+For Analysis 2, we need to generate 4 models using variations of parameters selected by Forwards Parameter Selection, Backwards Elimination, StepWise Selection, and a 
 personalized custom approach.
@@
 forward = ols_step_forward_p(fit_numeric, penter = 0.05, details = FALSE)
-
+#backwards
 backwards = ols_step_backward_p(fit_numeric, prem = 0.05, details = FALSE)
-
+#stepwise
 stepwise = ols_step_both_p(fit_numeric, pent = 0.05, prem =0.05, details = FALSE)
@@
 
-This step might not be necessary but could improve the quality of the model. Analysis shows a marginal improvement to R^2 and marginal deteriorate to PRESS Stat when rm'ing outliers.
+This step might not be necessary but could improve the quality of the model. Analysis shows a marginal improvement to R^2 and marginal deterioration to PRESS Stat when rm'ing outliers.
 
@@
 
+summary(transForward$model)
 ModelRMSE(transForward$model$residuals) #see defined functions at top of document
@@
 ```
+
+```{r Reduced Linearity Set}
+t1 = subset(transformed_numeric, select = -c(LotFrontage, MasVnrArea, GarageYrBlt, OverallQual, TotRmsAbvGrd, GarageCars, TotalBsmtSF, X1stFlrSF, X2ndFlrSF, FullBath )) #removal of largely correlated values to reduce multicollinearity (VIF /approx 1) and actually allow back-elimination to run, it wasn't running without a ton of errors without this.
+
+corrplot(cor(t1)) #visualize correlation to identify which plots are correlated. After elimiation, it should be fairly sparsely correlated.
+
+t1fit = lm(SalePrice ~. , data = t1)
+
+backt1 = ols_step_backward_p(t1fit, prem = 0.05, details = FALSE)
+forwardt1 = ols_step_forward_p(t1fit, penter = 0.05, details = FALSE)                #the p-values for these should be fiddled with to test a better selection set, although could be unnec. 
+stepwiset1 = ols_step_both_p(t1fit, pent = 0.05, prem =0.05, details = FALSE)
+
+#---------------------------------Summary Stats of the produced RL sets
+summary(backt1$model)
+vif(backt1$model)
+
+ModelRMSE(backt1$model$residuals)
+CVPress(backt1$model)
+#---------------------------------
+summary(forwardt1$model)
+vif(forwardt1$model)
+
+ModelRMSE(forwardt1$model$residuals)
+CVPress(forwardt1$model)
+#---------------------------------
+summary(stepwiset1$model)
+vif(stepwiset1$model)
+
+ModelRMSE(stepwiset1$model$residuals)
+CVPress(stepwiset1$model)
+
+```
+
+Now that we have generated 3 models (Need 4!!!) we can predict the saleprice on a test set of data, submit this modelled set to Kaggle to generate a Kaggle Score for the model.
+That is done as following;
+
+```{r}
+
+```

### 2022-12-10 rough_analysis.Rmd
Added prediction, and uploaded to Kaggle for a score. Score is on line 221

@@
+Analysis 1:
+
 For the first analysis, we are looking at houses are are only within the locale of [NAmes, Edwards, BrkSide neighborhoods] and at how Sale Price can possibly change
@@
 ```{r Reduced Linearity Set}
-t1 = subset(transformed_numeric, select = -c(LotFrontage, MasVnrArea, GarageYrBlt, OverallQual, TotRmsAbvGrd, GarageCars, TotalBsmtSF, X1stFlrSF, X2ndFlrSF, FullBath )) #removal of largely correlated values to reduce multicollinearity (VIF /approx 1) and actually allow back-elimination to run, it wasn't running without a ton of errors without this.
+t1 = subset(transformed_numeric, select = -c(LotFrontage, MasVnrArea, GarageYrBlt, OverallQual, TotRmsAbvGrd, GarageCars, TotalBsmtSF, X1stFlrSF, X2ndFlrSF, FullBath )) 
+#removal of largely correlated values to reduce multicollinearity (VIF /approx 1) and actually allow back-elimination to run,
+#it wasn't running without a ton of errors without this.
 
@@
 backt1 = ols_step_backward_p(t1fit, prem = 0.05, details = FALSE)
-forwardt1 = ols_step_forward_p(t1fit, penter = 0.05, details = FALSE)                #the p-values for these should be fiddled with to test a better selection set, although could be unnec. 
-stepwiset1 = ols_step_both_p(t1fit, pent = 0.05, prem =0.05, details = FALSE)
+forwardt1 = ols_step_forward_p(t1fit, penter = 0.05, details = FALSE)               #the p-values for these should be fiddled
+stepwiset1 = ols_step_both_p(t1fit, pent = 0.05, prem =0.05, details = FALSE)       #with to test a better selection set, although could be unnec.
 
@@
 
-Now that we have generated 3 models (Need 4!!!) we can predict the saleprice on a test set of data, submit this modelled set to Kaggle to generate a Kaggle Score for the model.
+Now that we have generated 3 models (Need 4!!!) we can predict the saleprice on a test set of data, submit this modelled set to Kaggle to generate a Kaggle Score for the model and analyze whether our approach was correct or not.
 That is done as following;
@@
 
+# build predictions from set:
+
+#since the original dataset is transformed, the testset needs to be transformed
+#as well to account for the change in base.
+test_housing$LotArea = log(test_housing$LotArea)
+
+back_pred = predict(backt1$model, test_housing)
+
+#Since the original dataset was transformed, we need to counter-transform to reobtain the
+#untransformed data.
+
+real_bp = exp(back_pred)
+
+#combine with ID and export as .csv
+
+real_bp_joined = data.frame(test_housing$Id, real_bp)
+colnames(real_bp_joined) = c("Id", "SalePrice")
+real_bp_joined[is.na(real_bp_joined)]<-10000 #if there are any NA, set them to arbitrary 10k price.
+
+write.csv(real_bp_joined, "./Kaggle_backt1_testset.csv", row.names = FALSE)
+
 ```
+
+The rudimentary approach of numeric/reduced linearity set receives a Kaggle score of 0.20

### 2022-12-10 rough_analysis.Rmd
Updated prediction models, added Kaggle scores from submitted material

@@
 backt1 = ols_step_backward_p(t1fit, prem = 0.05, details = FALSE)
-forwardt1 = ols_step_forward_p(t1fit, penter = 0.05, details = FALSE)               #the p-values for these should be fiddled
-stepwiset1 = ols_step_both_p(t1fit, pent = 0.05, prem =0.05, details = FALSE)       #with to test a better selection set, although could be unnec.
+forwardt1 = ols_step_forward_p(t1fit, penter = 0.05, details = FALSE)               #the p-values for these should be fiddled with, 
+stepwiset1 = ols_step_both_p(t1fit, pent = 0.05, prem =0.05, details = FALSE)
+
+mystery4thsetWIP
 
@@
 
+#--------------------------------------------- Backwards Elimination Prediction:
+
 back_pred = predict(backt1$model, test_housing)
@@
 
+#-------------------------------------------- Forwards Selection Prediction:
+
+forward_pred = predict(forwardt1$model, test_housing)
+real_forward = exp(forward_pred)
+real_fp_joined = data.frame(test_housing$Id, real_forward)
+real_fp_joined[is.na(real_fp_joined)]<-10000
+colnames(real_fp_joined) = c("Id", "SalePrice")
+write.csv(real_bp_joined, "./Kaggle_forwardt1_testset.csv", row.names = FALSE)
+
+#-------------------------------------------- Stepwise Selection Prediction:
+
+stepwise_pred = predict(stepwiset1$model, test_housing)
+real_step = exp(stepwise_pred)
+real_sp_joined = data.frame(test_housing$Id, real_step)
+real_sp_joined[is.na(real_sp_joined)]<-10000
+colnames(real_sp_joined) = c("Id", "SalePrice")
+write.csv(real_sp_joined, "./Kaggle_stepwiset1_testset.csv", row.names = FALSE)
+
 ```
 
-The rudimentary approach of numeric/reduced linearity set receives a Kaggle score of 0.20
+The rudimentary approach of numeric/reduced linearity set receives a Kaggle score of 0.20855.
+While is is interesting and good given the novel approach of the selection model, it's troubling to see that all 3 models returned the exact same Kaggle score, down to the last decimal.
+This may indicate that the models are adding/subtracting parameters to result in the exact same parameter list each time.
+This should be further investigated.

### 2022-12-10 rough_analysis.Rmd
Updated prediction models, added Kaggle scores from submitted material

@@
 
-The rudimentary approach of numeric/reduced linearity set receives a Kaggle score of 0.20855.
-While is is interesting and good given the novel approach of the selection model, it's troubling to see that all 3 models returned the exact same Kaggle score, down to the last decimal.
-This may indicate that the models are adding/subtracting parameters to result in the exact same parameter list each time.
-This should be further investigated.
+The rudimentary approach of numeric/reduced linearity set receives a Kaggle score of 0.20

### 2022-12-12 article.Rmd
Completed first part of Article Analysis

---
title: "Stats Project 2"
author: Abhay Sharma | AbhaySh4r.github.io
output:
  pdf_document: default
  html_notebook: default
---
```{r include=FALSE}
library(tidyverse)
```

\tableofcontents

\setlength\parindent{18pt}
\section{Introduction}

For this project, we are provided a housing data set from the website Kaggle that contains a large collection of parameters that are likely to be correlated with the Sale Price of their respective houses. Within this data set we find 79 parameters, some of which must ultimately be used to build a predictive model to extrapolate housing prices given a certain set of these parameters.

The work for this project has been divided into two separate analyses; the first being the generation of a linear model to select and analyze parameters indicating significant correlation between the Sale Price of the houses and the locale that they are in, and the second being the generation of a rudimentary feature selection model using forward selection, backwards elimination, and stepwise selection to predict the prices of houses, whose predictions are ultimately graded by a Kaggle score.

\section{Analysis 1}

For the first analysis, we are commissioned out to analyze and estimate how the Sale Price of houses in Ames Iowa correlate to the square footage in the house, as well as any interactions that might be present with respect to the regions the houses are in. The scope of the analysis focuses primarily on houses within the neighborhoods of \textit{North Ames, Edwards, and Brookside}.

\subsection{Model Generation and Analysis}
To generate an initial model, we will look at a rudimentary approach to linear regression to see what our data does;

```{r echo = TRUE, results = 'hide'}
housing = read.csv(file = "train.csv")
a1_set = housing %>% select(SalePrice, Neighborhood, GrLivArea) %>% filter( Neighborhood == c("NAmes", "Edwards", "BrkSide"))
fit <- lm(SalePrice ~ GrLivArea + Neighborhood + GrLivArea*Neighborhood, data = a1_set)
summary(fit)
#plot(fit)
#plot(a1_set$SalePrice, a1_set$GrLivArea)
```

We can see from visualizations of the plotted model and residuals of the analysis that a transform of variables would greatly improve the quality of the model and associated residuals. Applying a log - log transform and visualizing again, we see:

```{r echo = TRUE, results = 'hide'}
fit_transform <- lm(log(SalePrice) ~ log(GrLivArea) + Neighborhood + log(GrLivArea)*Neighborhood, data = a1_set)
summary(fit_transform)
confint(fit_transform)
#plot(log(a1_set$GrLivArea), log(a1_set$SalePrice))
#plot(fit_transform)
```

We find that the log-log transform has significantly reduced our residuals and given us a much better fit for the linear regression model, represented by bolstering our R^2 compared to the previous non-transformed model. We can see from the residual plots from the transformed fit that there are a few significantly high leverage/low residual points, and one out outlying point with a very high residual and leverage statistic.

We can also use these plots to analyse the assumptions for our linear model, from which we can see, after the log-log transform, there is not enough evidence to suggest a break in normality, visualized within the generated QQ plots, a statistically significant break in variance, visualized in the plot against both log-transformed variables, and that ...

\subsection{Parameter Interpretation}

Within the following table, we can see the parameters that our output from our transformed model. From this model, we can pick out the parameter estimates, and analyze which ones are statistically significant and how our final model might look considering significance.

[picture of R table]

In the table we can see the the parameters significance level, which provides a foundation for the interpretation for what each parameters value means in the scope of the linear model. It's also important to highlight that because the model was developed on a log-log transform model, parameters must be inverse-transformed to pull our their true values.

The first parameter presented with statistical significance, is the intercept value at \textbf{5.8}. This means that, in the absence of all other variables the y-intercept of this linear model is $2^{5.8} = \textbf{55}$. This intercept has a \textbf{95 percent confidence interval of (20.67, 158)}.

Following that, we have the reference slope value of \textit{GrLivArea} or the total square ft. in each house. We can interpret this value as, we expect to see a $2^0.82$ = \textbf{1.76 multiplicative increase in median Sale Price per doubling of SqFt.}. We have a \textbf{95 percent confidence interval for this increase of (1.53,2.04)}.

The next two parameters are critical as they describe the change in the intercept associated by each region within the model. For this model, the region \textit{BrookSide} is set as the reference region and generates two different modified intercepts to potentially describe any variation that is associated with the presence of multiple regions in the model. From the table, we can pick out that change in intercept for region \textit{Edwards} is not statistically significant compared against a default confidence level of $\alpha = 0.05$, so it might not be relevant to include in the model, whereas the change in the intercept for the \textit{North Ames} region is statistically significant with a \textbf{p-value of 0.003}, indicating that it's inclusion in the model explains a significant amount of the variation within the selected dataset. More importantly, the interpretation of this parameter explains that between \textit{BrookSide} and \textit{North Ames}, assuming for this explanation a constant slope, we can expect to see \textbf{an increased shift in the median sale prices of houses of $e^{2.82} = 16.77$}. The 95% confidence interval for this increase is \textbf{(2.585,107.7)}

Finally, the last two parameters within the model are the change in slope that might occur due to interactions between GvLivArea and Neighborhoods. Of these two paramters, we can see that only the change in slope between \textit{BrookSide} and \textit{North Ames} is statistically significant. The interpretation indicates that, due to the log-log transform, for every doubling of our SqFt, we expect to see a $2^{0.826+(-0.378)} = 2^{0.448} = \textbf{1.38}$ \textbf{multiplicative increase in the Sale Price of houses within the North Ames region}. We can see that the estimated slope of data associated with the \textit{North Ames} region has a smaller slope than the \text{BrookSide} region, indicating the prices of houses in \textit{North Ames} increases at smaller rate compared to the reference.

\subsection{Conclusion}

From a complete analysis of the parameters in the model, we can create a proper assessment of the different regions and how the pricing changes per region in the data. So far, what we've gathered is houses that are typically in the

\section{Appendix}

\subsection{Code for generating model}

### 2022-12-12 article.Rmd
Beginning second part of analysis

@@
 From a complete analysis of the parameters in the model, we can create a proper assessment of the different regions and how the pricing changes per region in the data.
-So far, what we've gathered is houses that are typically in the
+From the parameters, what we've gathered is houses that are typically in the N.
+Ames region start at higher pricing, but scale their pricing slower with respect to sq.
+ft.
+compared to houses that are within the Brookside region.
+Although the Edwards housing region has marginally varying statistics to the Brookside region, they are not statistically significant enough to indicate any explain any variation by themselves, and thus housing prices should follow the same trend.
+
+\section{Analysis 2}
+
+For the second analysis in this project,
 
@@
 
-\subsection{Code for generating model}
+\subsection{Code for generating linear model}
+
+```{r echo = TRUE, results = 'hide', fig.show= 'hide'}
+
+housing = read.csv(file = "train.csv")
+a1_set = housing %>% select(SalePrice, Neighborhood, GrLivArea) %>% filter( Neighborhood == c("NAmes", "Edwards", "BrkSide")) #pull dataset into R, select paramters for A1.
+fit <- lm(SalePrice ~ GrLivArea + Neighborhood + GrLivArea*Neighborhood, data = a1_set) #initial naive model, no transform
+summary(fit)
+
+#----------------
+
+fit_transform <- lm(log(SalePrice) ~ log(GrLivArea) + Neighborhood + log(GrLivArea)*Neighborhood, data = a1_set) #transformed model to improve residuals and assumptions
+summary(fit_transform)
+confint(fit_transform)
+
+```
+
+\subsection{Code for generating selection model}
+
+```{r}
+
+```

### 2022-12-12 article.Rmd
Added code to Appendix of article

@@
 library(tidyverse)
+library(plotly)
+library(car)
+library(caret)
+library(olsrr)
+library(corrplot)
 ```
@@
 
+\subsection{Useful Functions}
+
+```{r RMSE function}
+ModelRMSE <- function(res){
+  retRMSE <- sqrt(mean(res^2))
+  return(retRMSE)
+}
+```
+
+```{r CVPress function}
+CVPress <- function(input_model){
+  pred_res = resid(input_model)/(1 - lm.influence(input_model)$hat)
+  press <- sum(pred_res^2)
+  return(press)
+}
+```
+
 \subsection{Code for generating linear model}
@@
 housing = read.csv(file = "train.csv")
-a1_set = housing %>% select(SalePrice, Neighborhood, GrLivArea) %>% filter( Neighborhood == c("NAmes", "Edwards", "BrkSide")) #pull dataset into R, select paramters for A1.
-fit <- lm(SalePrice ~ GrLivArea + Neighborhood + GrLivArea*Neighborhood, data = a1_set) #initial naive model, no transform
+test_housing = read.csv(file = "test.csv")
+numeric_housing = housing %>% select_if(is.numeric)
+#pull dataset into R, select paramters for A1.
+a1_set = housing %>% select(SalePrice, Neighborhood, GrLivArea) %>%
+  filter( Neighborhood == c("NAmes", "Edwards", "BrkSide")) 
+#initial naive model, no transform
+fit <- lm(SalePrice ~ GrLivArea + Neighborhood + GrLivArea*Neighborhood, data = a1_set)
+
 summary(fit)
@@
 
-fit_transform <- lm(log(SalePrice) ~ log(GrLivArea) + Neighborhood + log(GrLivArea)*Neighborhood, data = a1_set) #transformed model to improve residuals and assumptions
+#transformed model to improve residuals and assumptions
+fit_transform <- lm(log(SalePrice) ~ log(GrLivArea) + Neighborhood +
+                      log(GrLivArea)*Neighborhood, data = a1_set)
+
 summary(fit_transform)
@@
 
-```{r}
+```{r echo = TRUE, results = 'hide', fig.show= 'hide'}
+fit_numeric = lm(SalePrice ~., data = housing %>% select_if(is.numeric))
+transformed_numeric = numeric_housing
+transformed_numeric$SalePrice = log(transformed_numeric$SalePrice)
+transformed_numeric$LotArea = log(transformed_numeric$LotArea)
+t1 = subset(transformed_numeric, select = -c(LotFrontage, MasVnrArea, GarageYrBlt,
+                                             OverallQual, TotRmsAbvGrd, GarageCars,
+                                             TotalBsmtSF, X1stFlrSF, X2ndFlrSF, FullBath ))
+
+corrplot(cor(t1)) #visualize correlation to identify which plots are correlated.
+#After elimiation, it should be fairly sparsely correlated.
+
+t1fit = lm(SalePrice ~. , data = t1)
+
+#the p-values for these should be fiddled with, 
+backt1 = ols_step_backward_p(t1fit, prem = 0.05, details = FALSE)
+forwardt1 = ols_step_forward_p(t1fit, penter = 0.05, details = FALSE)               
+stepwiset1 = ols_step_both_p(t1fit, pent = 0.05, prem =0.05, details = FALSE)
+
+#---------------------------------Summary Stats of the produced RL sets
+summary(backt1$model)
+vif(backt1$model)
+
+ModelRMSE(backt1$model$residuals)
+CVPress(backt1$model)
+#---------------------------------
+summary(forwardt1$model)
+vif(forwardt1$model)
+
+ModelRMSE(forwardt1$model$residuals)
+CVPress(forwardt1$model)
+#---------------------------------
+summary(stepwiset1$model)
+vif(stepwiset1$model)
+
+ModelRMSE(stepwiset1$model$residuals)
+CVPress(stepwiset1$model)
+
+# build predictions from set:
+
+#since the original dataset is transformed, the testset needs to be transformed
+#as well to account for the change in base.
+test_housing$LotArea = log(test_housing$LotArea)
+
+#--------------------------------------------- Backwards Elimination Prediction:
+
+back_pred = predict(backt1$model, test_housing)
+
+#Since the original dataset was transformed, we need to counter-transform to reobtain the
+#untransformed data.
+
+real_bp = exp(back_pred)
+
+#combine with ID and export as .csv
+
+real_bp_joined = data.frame(test_housing$Id, real_bp)
+colnames(real_bp_joined) = c("Id", "SalePrice")
+#if there are any NA, set them to arbitrary 10k price. 
+real_bp_joined[is.na(real_bp_joined)]<-10000
+
+write.csv(real_bp_joined, "./Kaggle_backt1_testset.csv", row.names = FALSE)
+
+#-------------------------------------------- Forwards Selection Prediction:
+
+forward_pred = predict(forwardt1$model, test_housing)
+real_forward = exp(forward_pred)
+real_fp_joined = data.frame(test_housing$Id, real_forward)
+real_fp_joined[is.na(real_fp_joined)]<-10000
+colnames(real_fp_joined) = c("Id", "SalePrice")
+write.csv(real_bp_joined, "./Kaggle_forwardt1_testset.csv", row.names = FALSE)
+
+#-------------------------------------------- Stepwise Selection Prediction:
+
+stepwise_pred = predict(stepwiset1$model, test_housing)
+real_step = exp(stepwise_pred)
+real_sp_joined = data.frame(test_housing$Id, real_step)
+real_sp_joined[is.na(real_sp_joined)]<-10000
+colnames(real_sp_joined) = c("Id", "SalePrice")
+write.csv(real_sp_joined, "./Kaggle_stepwiset1_testset.csv", row.names = FALSE)
 

### 2022-12-12 article.Rmd
Updated first analysis

@@
 #plot(a1_set$SalePrice, a1_set$GrLivArea)
+
+#put the plots here
 ```
@@
 #plot(fit_transform)
+
+#put the plots here
 ```
@@
 
+ModelRMSE(fit$residuals) #RMSE value of 33802
+ModelRMSE(fit_transform$residuals) # RMSE Value of 0.1973
 ```

### 2022-12-12 StatsProject_draft_Caro.Rmd
Custom Model Trials

@@
 ```{r}
-train <- read.csv("train.csv")
-test <- read.csv("test.csv")
+train <- read.csv("train.csv", header=TRUE, stringsAsFactors=TRUE)
+test <- read.csv("test.csv", header=TRUE, stringsAsFactors=TRUE)
 
@@
 summary(test_a1)
+
+str(train_a1)
 ```
 ## EDA
+
 ```{r}
@@
 
-# Linear Model
+## Linear Model 
 ```{r}
-fit <- lm(log(SalePrice) ~ log(GrLivArea) + Neighborhood + GrLivArea*Neighborhood, data = train_a1)
-summary(fit)
-confint(fit)
+fit1 <- lm(log(SalePrice) ~ log(GrLivArea) + Neighborhood + GrLivArea*Neighborhood, data = train_a1)
+summary(fit1)
+confint(fit1)
 
-plot(fit)
+plot(fit1)
+
+hist(fit1$residuals, col = "blue", main = "Histogram of Residuals")
+plot(fit1$fitted.values,fit1$residuals, main = "Plot of Residuals v. Fitted Values")
+sqrt(mean(fit1$residuals^2)) #RMSE
 ```
-# ANOVA 
+```{r}
+
+```
+
+## ANOVA 
 ```{r}
@@
 # histogram of residuals 
-h <- hist(fit$residuals, breaks = 10, density = 10,col = "lightgray",main = "Residuals") 
-xfit <- seq(min(fit$residuals), max(fit$residuals), length = 40) 
-yfit <- dnorm(xfit, mean = mean(fit$residuals), sd = sd(fit$residuals)) 
-yfit <- yfit * diff(h$mids[1:2]) * length(fit$residuals) 
+h <- hist(fit1$residuals, breaks = 10, density = 10,col = "lightgray",main = "Residuals") 
+xfit <- seq(min(fit1$residuals), max(fit1$residuals), length = 40) 
+yfit <- dnorm(xfit, mean = mean(fit1$residuals), sd = sd(fit1$residuals)) 
+yfit <- yfit * diff(h$mids[1:2]) * length(fit1$residuals) 
 ```
+
+##remove outliers
+```{r}
+
+```
+
+# ANALYSIS 2: MODELS
+
+## EDA
+```{r}
+str(train)
+summary(train)
+```
+##
+### Missing data & Duplicates
+- NA means something in following: Alley, BsmtQual, BsmtCond, BsmtExposure, BsmtFinType1,BsmtFinType2, FireplaceQu, GarageType, GarageFinish, GarageQual, GarageCond, PoolQC, Fence, MiscFeature
+- Electrical has NAs but seems important? 
+```{r}
+colSums(is.na(train)) != 0
+
+# remove columns with NAs that have no meaning (from data description)
+train_clean = subset(train, select= -c(LotFrontage,MasVnrType, MasVnrArea))
+
+```
+
+```{r}
+train[duplicated(train),]
+
+```
+## Look at distribution of SalePrice &  LotArea
+
+## Replace N/A 
+```{r}
+
+train_clean[is.na(train_clean)] = "None"
+summary(train_clean )
+```
+
+##  Feature Selection 
+```{r}
+library(caret)
+# Feature Selection
+# We need to find features which are important for the model.
+
+# Setting Seed to ensure results are repeatable.
+set.seed(7)
+
+# prepare training scheme
+control <- trainControl(method="repeatedcv", number=10, repeats=3)
+# train the model 
+model <- train(SalePrice~., data=train, method="lvq", preProcess="scale", trControl=control)
+# estimate variable importance
+importance <- varImp(model, scale=FALSE)
+# summarize importance
+print(importance)
+# plot importance
+plot(importance)
+```
+## Create Model 
+```{r}
+fit2 = lm(SalePrice~LotArea , data= train)
+summary(fit2)
+```
+
+## Forward Selection
+
+```{r}
+library(olsrr)
+ols_step_forward_p(fit2, penter = 0.05, details = TRUE)
+
+```
+
+## Backwards Elimination 
+```{r}
+ols_step_backward_p(fit, prem = 0.05, details = TRUE)
+
+```
+
+## Stepwise Selection 
+```{r}
+ols_step_both_p(fit, prem = 0.05, pent = 0.05, details = FALSE)
+
+```
+
+## Custom Model

### 2022-12-12 rough_analysis.Rmd
Custom Model Trials

--- 2022-12-10 rough_analysis.Rmd
@@
 
-For the first analysis, we are looking at houses are are only within the locale of [NAmes, Edwards, BrkSide neighborhoods] and at how Sale Price can possibly change
-with respect to the Size of the living area and the Neighborhood in which the property is located, which can be visualized with the equation:
+## Restatement of the Problem 
+Estimate how SalesPrice of the house is related to the square footage of the living area of the house & if SalesPrice (and its relationship to square footage) depends on which neighborhood the house is located in.
+We are only interested at looking at houses in the NAmes, Edwards & BrkSide neighborhoods.
+This relationship can be visualized with the equation:
 
@@
 a1_set %>% ggplot(aes(x = SalePrice/10000, fill = Neighborhood)) + geom_histogram(bins =20)
+
+a1_set %>% ggplot(aes(x = GrLivArea, fill = Neighborhood)) + geom_histogram(bins =20)
+
 ```
+The histograms show both GrLivArea and Sales Price having a right skew distribution.
+We will examine different log transformations to see if we can obtain a more normal distribution suitable for our model.
+
+## Log Transforms 
+```{r}
+# histograms with log transform on each individual variables
+train_a1 %>% ggplot(aes(x = log(SalePrice/10000), fill = Neighborhood)) + geom_histogram(bins =20)
+
+train_a1 %>% ggplot(aes(x = log(GrLivArea), fill = Neighborhood)) + geom_histogram(bins =20)
+
+train_a1 %>% ggplot(aes(x = log(GrLivArea), y = SalePrice/1000, color = Neighborhood)) + geom_point() + stat_smooth(method = "lm")
+
+train_a1 %>% ggplot(aes(x = (GrLivArea), y = log(SalePrice/1000), color = Neighborhood)) + geom_point() + stat_smooth(method = "lm")
+
+train_a1 %>% ggplot(aes(x = log(GrLivArea), y = log(SalePrice/1000), color = Neighborhood)) + geom_point() + stat_smooth(method = "lm")
+```
+Using a log transform on the GrLivArea and SalePrice variables, we achieve a more normal distribution for each variable which will be more conducive to use in our model.
 
@@
 ```
+## Linear Models
+
+From a visual inspection of the Cook's D and residual plot, we notice there are 3 outliers: 
+  - ID 54
+  - ID 61, 
+  - ID 114
+```{r}
+fit1 <- lm(SalePrice ~ GrLivArea + Neighborhood + GrLivArea*Neighborhood, data = a1_set)
+summary(fit1)
+confint(fit1)
+
+plot(fit1)
+
+hist(fit1$residuals, col = "blue", main = "Histogram of Residuals")
+sqrt(mean(fit1$residuals^2)) #RMSE
+```
+
+### Remove Outliers 
+```{r}
+head(a1_set)
+a1_set2 = housing
+a1_set2 = a1_set2 [(!(a1_set2 $Id == "54") & !(a1_set2 $Id == "61") & !(a1_set2 $Id == "114") ),]
+head(a1_set2)
+
+a1_set2 = a1_set2 %>% select(SalePrice, Neighborhood, GrLivArea) %>% filter( Neighborhood == c("NAmes", "Edwards", "BrkSide"))
+head(a1_set2)
+```
+
+### Fit model without outliers 
+```{r}
+fit2 <- lm(log(SalePrice) ~ log(GrLivArea) + Neighborhood + GrLivArea*Neighborhood, data = a1_set2)
+summary(fit2)
+confint(fit2)
+
+plot(fit2)
+
+hist(fit2$residuals, col = "blue", main = "Histogram of Residuals")
+sqrt(mean(fit2$residuals^2)) #RMSE
+```
 
@@
 #bad approach, maybe, I can't get it to work 
-#train.control = trainControl(method = "cv", number = 10)
-#step.model = train(SalePrice ~.-GarageArea, data = housing %>% select_if(is.numeric) %>% drop_na(), method = "leapBackward", trControl = train.control)
+train.control = trainControl(method = "cv", number = 10)
+step.model = train(SalePrice ~.-GarageArea, data = housing %>% select_if(is.numeric) %>% drop_na(), method = "leapBackward", trControl = train.control)
+pred(step.model, housing)
 #step.model$modelInfo
@@
 ```{r}
-#install.packages("olsrr")
+install.packages("olsrr")
 
@@
 
+transForward
 summary(transForward$model)
@@
 
-mystery4thsetWIP
+forwardt1
+backt1
+stepwiset1
+#mystery4thsetWIP
 
@@
 CVPress(stepwiset1$model)
+
+```
+## Custom Model 
+```{r}
+# Change categorical values to numeric
+housing2 = housing
+housing2$Neighborhood <- as.numeric(factor(housing2$Neighborhood,
+                                                        levels = c("Blmngtn", "Blueste", "BrDale"),
+                                                        labels = c(2,1,0), ordered = TRUE))
+housing2$LotConfig <- as.numeric(factor(housing2$LotConfig,
+                                                        levels = c("Inside", "Corner", "CulDSac", "FR2", "FR3"),
+                                                        labels = c(4,3,2,1,0), ordered = TRUE))
+housing2$ExterQual <- as.numeric(factor(housing2$ExterQual,
+                                                        levels = c("Ex", "Gd", "TA", "Fa", "Po"),
+                                                        labels = c(4, 3, 2,1,0), ordered = TRUE))
+housing2$BsmtQual <- as.numeric(factor(housing2$BsmtQual,
+                                                        levels = c("Ex", "Gd", "TA", "Fa", "Po"),
+                                                        labels = c(4, 3, 2,1,0), ordered = TRUE))
+
+```
+```{r}
+# Only look at Normal Sales 
+normal_housing = housing 
+normal_set = normal_housing %>% select(SaleCondition) %>% filter( SaleCondition == c("Normal"))
+normal_housing = normal_housing %>% select_if(is.numeric)
+```
+
+```{r}
+t2 = subset(transformed_numeric, select = -c(LotFrontage, MasVnrArea, GarageYrBlt, OverallQual, TotRmsAbvGrd, GarageCars, TotalBsmtSF, X1stFlrSF, X2ndFlrSF, FullBath )) 
+#removal of largely correlated values to reduce multicollinearity (VIF /approx 1) and actually allow back-elimination to run,
+#it wasn't running without a ton of errors without this.
+
+corrplot(cor(t2)) #visualize correlation to identify which plots are correlated. After elimiation, it should be fairly sparsely correlated.
+
+t2fit = lm(SalePrice ~. , data = t2)
+
+backt2 = ols_step_backward_p(t2fit, prem = 0.05, details = FALSE)
+forwardt2 = ols_step_forward_p(t2fit, penter = 0.05, details = FALSE)               #the p-values for these should be fiddled with, 
+stepwiset2 = ols_step_both_p(t2fit, pent = 0.05, prem =0.05, details = FALSE)
+
+forwardt2
+backt2
+stepwiset2
+#mystery4thsetWIP
+
+#---------------------------------Summary Stats of the produced RL sets
+summary(backt2$model)
+vif(backt2$model)
+
+ModelRMSE(backt2$model$residuals)
+CVPress(backt2$model)
+#---------------------------------
+summary(forwardt2$model)
+vif(forwardt2$model)
+
+ModelRMSE(forwardt2$model$residuals)
+CVPress(forwardt2$model)
+#---------------------------------
+summary(stepwiset2$model)
+vif(stepwiset2$model)
+
+ModelRMSE(stepwiset2$model$residuals)
+CVPress(stepwiset2$model)
 

### 2022-12-12 rough_analysis.Rmd
Custom Model Add Prediction csv files

@@
 ## Custom Model
+
 ```{r}
@@
 normal_housing = normal_housing %>% select_if(is.numeric)
+
+normal_housing$SalePrice = log(normal_housing$SalePrice)
+normal_housing$GrLivArea = log(normal_housing$GrLivArea)
+
 ```
@@
 ```{r}
-t2 = subset(transformed_numeric, select = -c(LotFrontage, MasVnrArea, GarageYrBlt, OverallQual, TotRmsAbvGrd, GarageCars, TotalBsmtSF, X1stFlrSF, X2ndFlrSF, FullBath )) 
+t2 = subset(normal_housing, select = -c(LotFrontage, MasVnrArea, GarageYrBlt, OverallQual, TotRmsAbvGrd, GarageCars, TotalBsmtSF, X1stFlrSF, X2ndFlrSF, FullBath )) 
 #removal of largely correlated values to reduce multicollinearity (VIF /approx 1) and actually allow back-elimination to run,
@@
 
+#-------------------------------------------- Custom Model Prediction:
+
+# Backwards Elimination
+test_housing$GrLivArea = log(test_housing$GrLivArea)
+back_pred2 = predict(backt2$model, test_housing) 
+head(back_pred2)
+#Since the original dataset was transformed, we need to counter-transform to reobtain the
+#untransformed data.
+
+real_bp2 = exp(back_pred2)
+
+#combine with ID and export as .csv
+
+real_bp_joined2 = data.frame(test_housing$Id, real_bp2)
+colnames(real_bp_joined2) = c("Id", "SalePrice")
+real_bp_joined2[is.na(real_bp_joined2)]<-10000 #if there are any NA, set them to arbitrary 10k price.
+
+head(real_bp_joined2)
+write.csv(real_bp_joined2, "./Kaggle_backt2_testset.csv", row.names = FALSE)
+
+# Forward Selection
+forward_pred2 = predict(forwardt2$model, test_housing)
+real_forward2 = exp(forward_pred2)
+real_fp_joined2 = data.frame(test_housing$Id, real_forward2)
+real_fp_joined2[is.na(real_fp_joined2)]<-10000
+colnames(real_fp_joined2) = c("Id", "SalePrice")
+write.csv(real_bp_joined2, "./Kaggle_forwardt2_testset.csv", row.names = FALSE)
+
+# Stepwise Selection 
+stepwise_pred2 = predict(stepwiset2$model, test_housing)
+real_step2 = exp(stepwise_pred2)
+real_sp_joined2 = data.frame(test_housing$Id, real_step2)
+real_sp_joined2[is.na(real_sp_joined2)]<-10000
+colnames(real_sp_joined2) = c("Id", "SalePrice")
+write.csv(real_sp_joined2, "./Kaggle_stepwiset2_testset.csv", row.names = FALSE)
+
 ```

### 2022-12-12 article.Rmd
fixes to article and rough analysis, added log transform to grlivearea in prediction set

@@
 We can see from the residual plots from the transformed fit that there are a few significantly high leverage/low residual points, and one out outlying point with a very high residual and leverage statistic.
+We can also verify from the adjusted $R^2$ and RMSE from each model that the transformed model fits the data much better than the a non-transformed model.
 
@@
 ModelRMSE(fit_transform$residuals) # RMSE Value of 0.1973
+
+# Internal CV Press of Models:
+
+train.control1 = trainControl(method = "cv", number = 10)
+model1 <- train(SalePrice ~ GrLivArea + Neighborhood + GrLivArea*Neighborhood, data = a1_set, method = "lm", trControl = train.control1)
+CVPress(model1$model)# doesn't work atm
+
 ```

### 2022-12-12 rough_analysis.Rmd
fixes to article and rough analysis, added log transform to grlivearea in prediction set

--- 2022-12-10 rough_analysis.Rmd
@@
 transformed_numeric$LotArea = log(transformed_numeric$LotArea)
+transformed_numeric$GrLivArea = log(transformed_numeric$GrLivArea)
 
@@
 test_housing$LotArea = log(test_housing$LotArea)
+test_housing$GrLivArea = log(test_housing$GrLivArea)
 
@@
 
-The rudimentary approach of numeric/reduced linearity set receives a Kaggle score of 0.20
+The rudimentary approach of numeric/reduced linearity set receives a Kaggle score of 0.20141.
+While is is interesting and good given the novel approach of the selection model, it's troubling to see that all 3 models returned the exact same Kaggle score, down to the last decimal.
+This may indicate that the models are adding/subtracting parameters to result in the exact same parameter list each time.
+This should be further investigated.

### 2022-12-12 rough_analysis.Rmd

--- 2022-12-12 rough_analysis.Rmd
@@
 
-The rudimentary approach of numeric/reduced linearity set receives a Kaggle score of 0.20855.
+The rudimentary approach of numeric/reduced linearity set receives a Kaggle score of 0.20141.
 While is is interesting and good given the novel approach of the selection model, it's troubling to see that all 3 models returned the exact same Kaggle score, down to the last decimal.

### 2022-12-12 article.Rmd
Updates to article.Rmd

@@
 ---
+
 ```{r include=FALSE}
@@
 
+```{=tex}
 \setlength\parindent{18pt}
 \section{Introduction}
-
+```
 For this project, we are provided a housing data set from the website Kaggle that contains a large collection of parameters that are likely to be correlated with the Sale Price of their respective houses.
@@
 \subsection{Model Generation and Analysis}
+
 To generate an initial model, we will look at a rudimentary approach to linear regression to see what our data does;
@@
 
-We find that the log-log transform has significantly reduced our residuals and given us a much better fit for the linear regression model, represented by bolstering our R^2 compared to the previous non-transformed model.
+We find that the log-log transform has significantly reduced our residuals and given us a much better fit for the linear regression model, represented by bolstering our R\^2 compared to the previous non-transformed model.
 We can see from the residual plots from the transformed fit that there are a few significantly high leverage/low residual points, and one out outlying point with a very high residual and leverage statistic.
@@
 
-For the second analysis in this project,
+For the second analysis in this project, we were tasked to generate 4 models using variations of parameters selected by Forward Selection, Backwards Elimination, Stepwise Selection, and a personalized approach.
+Using these paramters, we can generate Adjusted R\^2 values, CV Press statistics, and finally submit our model to the Kaggle website to obtain a "Kaggle Score" for each model.
+
+To improve the quality of our model, we decided to remove outliers as analaysis shows marginal improvements to R\^2 and marginal deterioration to the Press Statistic. We notice the following outliers:
+
+-   Excessively Expensive \> 700k SalePrice: ID #692 & \# 1183 -
+
+-   Excessively Large \> 100k sq ft.: ID #314, #226, #256, #707
+
+Next, we removed the following highly correlated variables to reduce multicollinearity: LotFrontage, MasVnrArea, GarageYrBlt, OverallQual, TotRmsAbvGrd, GarageCars, TotalBsmtSF, X1stFlrSF, X2ndFlrSF, FullBath.
+In the correlation matrix, we can see which plots are correlated.
+After the elimination of the variables mentioned, we see more fairly spare correlated variables.
+
+```{r}
+corrplot(cor(t1))
+```
+
+## Model Results
+
+| Model                | Adjusted R\^2 | RMSE      | CVPress  |
+|----------------------|---------------|-----------|----------|
+| Forward Selection    | 0.8333        | 0.1620974 | 43.77074 |
+| Backward Elimination | 0.8333        | 0.1620974 | 43.77074 |
+| Stepwise Selection   | 0.8333        | 0.1620974 | 43.77074 |
+
+The rudimentary approach of numeric/reduced linearity set receives a Kaggle score of 0.20141.
+While is is interesting and good given the novel approach of the selection model, it's troubling to see that all 3 models returned the exact same Kaggle score, down to the last decimal.
+This may indicate that the models are adding/subtracting parameters to result in the exact same parameter list each time.
+This should be further investigated.
 

### 2022-12-12 article.Rmd
add plots to article

@@
 
+```{r}
+
+a1_set %>% ggplot(aes(x = (GrLivArea), y = SalePrice/1000, color = Neighborhood)) + geom_point() + stat_smooth(method = "lm")
+
+a1_set %>% ggplot(aes(x = SalePrice/10000, fill = Neighborhood)) + geom_histogram(bins =20)
+
+a1_set %>% ggplot(aes(x = GrLivArea, fill = Neighborhood)) + geom_histogram(bins =20)
+```
+
 We can see from visualizations of the plotted model and residuals of the analysis that a transform of variables would greatly improve the quality of the model and associated residuals.
@@
 #put the plots here
+plot(fit_transform)
 ```
@@
 
+```{r}
+plot(t1fit)
+```
+
 To improve the quality of our model, we decided to remove outliers as analaysis shows marginal improvements to R\^2 and marginal deterioration to the Press Statistic. We notice the following outliers:
 
--   Excessively Expensive \> 700k SalePrice: ID #692 & \# 1183 -
+-   Excessively Expensive \> 700k SalePrice: ID #692 & \# 1183
 
@@
 ```
+
+Stepwise Selection
+
+Regression model:
+
+Mean(SalePrice) = b0 + b1(OverallQual) + b2(OverallCond) + b3(YearBuilt) + b4(
 

### 2022-12-12 article.Rmd
add plots to article

@@
 ```{r}
-plot(t1fit)
+plot(fit_numeric)
+```
+```{r}
+plot(transformed_fit) 
 ```
@@
 ```
+
+```{r}
+#I'm not sure if this is the best way to do it, but it highlights the requirement of the transform
+
+boxplot(numeric_housing) #<-visualize outliers
+
+#filtered_nh = numeric_housing[-c(692, 1183, 314, 336, 256, 707), ] #filters out outliers 
+#filtered_nh$SalePrice = log(filtered_nh$SalePrice) 
+#filtered_nh$LotArea = log(filtered_nh$LotArea)
+
+transformed_numeric = numeric_housing
+transformed_numeric$SalePrice = log(transformed_numeric$SalePrice)
+transformed_numeric$LotArea = log(transformed_numeric$LotArea)
+transformed_numeric$GrLivArea = log(transformed_numeric$GrLivArea)
+
+boxplot(transformed_numeric)
+
+transformed_fit = lm(SalePrice ~., data = transformed_numeric)
+
+transForward = ols_step_forward_p(transformed_fit, penter = 0.05, details = FALSE)
+
+transForward
+summary(transForward$model)
+ModelRMSE(transForward$model$residuals) #see defined functions at top of document
+CVPress(transForward$model)

### 2022-12-12 article.Rmd
update article

@@
 
-To improve the quality of our model, we decided to remove outliers as analaysis shows marginal improvements to R\^2 and marginal deterioration to the Press Statistic. We notice the following outliers:
+To improve the quality of our model, we look at outliers as analaysis shows marginal improvements to R\^2 and marginal deterioration to the Press Statistic. We notice the following outliers:
 
@@
 -   Excessively Large \> 100k sq ft.: ID #314, #226, #256, #707
+
+However, removing them did not improve the model, so we decided to leave them in.
 
@@
 
-Mean(SalePrice) = b0 + b1(OverallQual) + b2(OverallCond) + b3(YearBuilt) + b4(
+Mean(SalePrice) = b0 + b1(LotArea) + b2(OverallCond) + b3(YearBuilt) + b4(YearRemodAdd) + b5(BsmtFinSF1) + b6(BsmtFinSF2) + b7(BsmtFinSF3) + b8(GrLivArea) + b9(BsmtFullBath) + b10(KitchenAbvGr) + b11(Fireplaces) + b12(GarageArea) + b13(WoodDeckSF) + b14(EnclosedPorch) + b15(ScreenPorch) + b16(PoolArea) + b17(YrSold)
 

### 2022-12-12 StatsProject_draft_Caro.Rmd
Add RShiny App Files

@@
 
-Goal: Estimate how SalesPrice of the house is related to the square footage of the living area of the house & if SalesPrice (and its relationship to square footage) depends on which neighborhood the house is located in.
+## Restatement of the Problem 
+Estimate how SalesPrice of the house is related to the square footage of the living area of the house & if SalesPrice (and its relationship to square footage) depends on which neighborhood the house is located in.
 We are only interested at looking at houses in the NAmes, Edwards & BrkSide neighborhoods.
@@
 
+From an initial examination of the scatter plots and histograms,
+
 ```{r}
@@
 ## Linear Model
+
+From a visual inspection of the Cook's D and residual plot, we notice there are 3 outliers: 
 ```{r}

### 2022-12-12 HousingApp/app.R

@@ -1,0 +1,61 @@
+#
+# This is a Shiny web application. You can run the application by clicking
+# the 'Run App' button above.
+#
+# Find out more about building applications with Shiny here:
+#
+#    http://shiny.rstudio.com/
+#
+
+library(shiny)
+
+# Define UI for application that draws a histogram
+ui <- fluidPage(
+
+    # Application title
+    titlePanel("Price of Home vs. Square Footage Based on Neighborhood"),
+
+    # Sidebar with a slider input for number of bins 
+    sidebarLayout(
+        sidebarPanel(
+          fileInput("file1", "Choose CSV File",
+                    accept = c(
+                      "text/csv",
+                      "text/comma-separated-values,text/plain",
+                      ".csv")
+          ),
+            selectInput("neighborhood", 
+                        label="Please select a Neighborhood to View",
+                       choices=c("NAmes","Edwards", "BrkSide" ))
+        ),
+
+        # Show a plot of the generated distribution
+        mainPanel(
+           plotOutput("distPlot")
+        )
+    )
+)
+
+# Define server logic required to draw a histogram
+server <- function(input, output) {
+    library(readr)
+    output$distPlot <- renderPlot({
+      housing <-- input$file1
+      read.csv(housing$datapath, header = input$header)
+      
+     # housing = read.csv("Stats1Project/train.csv")
+      if(input$neighborhood == "NAmes"){
+       names= housing %>% filter(Neighborhood == "NAmes") %>% ggplot(aes(x = (GrLivArea), y = SalePrice/1000)) + geom_point() + ggtitle("NAmes Neighborhood Price of Home vs. Square Footage")
+        
+      } else if(input$neighborhood == "Edwards"){
+        edwards= housing %>% filter(Neighborhood == "Edwards") %>% ggplot(aes(x = (GrLivArea), y = SalePrice/1000)) + geom_point() + ggtitle("Edwards Neighborhood Price of Home vs. Square Footage")
+        
+      } else if(input$neighborhood == "Brkside"){
+        brk= housing %>% filter(Neighborhood == "Brkside") %>% ggplot(aes(x = (GrLivArea), y = SalePrice/1000)) + geom_point() + ggtitle("Brkside Neighborhood Price of Home vs. Square Footage")
+
+      }
+    })
+}
+
+# Run the application 
+shinyApp(ui = ui, server = server)

### 2022-12-12 HousingApp/app.R
Add working Rshiny files

@@ -39,21 +39,31 @@ ui <- fluidPage(
 # Define server logic required to draw a histogram
 server <- function(input, output) {
     library(readr)
+    library(ggplot2)
+    library(dplyr)
+  
+  plot_data <- reactive({
+    inFile = input$file1
+    housing <-- read.csv(inFile$datapath)
+    
+    plot
+  }) 
     output$distPlot <- renderPlot({
-      housing <-- input$file1
-      read.csv(housing$datapath, header = input$header)
-      
-     # housing = read.csv("Stats1Project/train.csv")
       if(input$neighborhood == "NAmes"){
-       names= housing %>% filter(Neighborhood == "NAmes") %>% ggplot(aes(x = (GrLivArea), y = SalePrice/1000)) + geom_point() + ggtitle("NAmes Neighborhood Price of Home vs. Square Footage")
+        
+        plot = housing %>% filter(Neighborhood == "NAmes") %>% ggplot(aes(x = (GrLivArea), y = SalePrice/1000)) + geom_point() + ggtitle("NAmes Neighborhood Price of Home vs. Square Footage")
         
       } else if(input$neighborhood == "Edwards"){
-        edwards= housing %>% filter(Neighborhood == "Edwards") %>% ggplot(aes(x = (GrLivArea), y = SalePrice/1000)) + geom_point() + ggtitle("Edwards Neighborhood Price of Home vs. Square Footage")
+        plot = housing %>% filter(Neighborhood == "Edwards") %>% ggplot(aes(x = (GrLivArea), y = SalePrice/1000)) + geom_point() + ggtitle("Edwards Neighborhood Price of Home vs. Square Footage")
         
       } else if(input$neighborhood == "Brkside"){
-        brk= housing %>% filter(Neighborhood == "Brkside") %>% ggplot(aes(x = (GrLivArea), y = SalePrice/1000)) + geom_point() + ggtitle("Brkside Neighborhood Price of Home vs. Square Footage")
-
+        plot = housing %>% filter(Neighborhood == "Brkside") %>% ggplot(aes(x = (GrLivArea), y = SalePrice/1000)) + geom_point() + ggtitle("Brkside Neighborhood Price of Home vs. Square Footage")
+        
       }
+      plot
+     
+     # housing = read.csv("Stats1Project/train.csv")
+
     })
 }
 

### 2022-12-12 article.Rmd
Add RShiny App Files
updates to analysis 2 and selection models

--- 2022-12-12 article.Rmd
@@
 ---
-
 ```{r include=FALSE}
@@
 
-```{=tex}
 \setlength\parindent{18pt}
 \section{Introduction}
-```
+
 For this project, we are provided a housing data set from the website Kaggle that contains a large collection of parameters that are likely to be correlated with the Sale Price of their respective houses.
@@
 \subsection{Model Generation and Analysis}
-
 To generate an initial model, we will look at a rudimentary approach to linear regression to see what our data does;
 
-```{r echo = TRUE, results = 'hide'}
+```{r echo = TRUE, results = 'hide', warning=FALSE}
 housing = read.csv(file = "train.csv")
+numeric_housing = housing %>% select_if(is.numeric)
 a1_set = housing %>% select(SalePrice, Neighborhood, GrLivArea) %>% filter( Neighborhood == c("NAmes", "Edwards", "BrkSide"))
@@
 #put the plots here
-```
-
-```{r}
-
-a1_set %>% ggplot(aes(x = (GrLivArea), y = SalePrice/1000, color = Neighborhood)) + geom_point() + stat_smooth(method = "lm")
-
-a1_set %>% ggplot(aes(x = SalePrice/10000, fill = Neighborhood)) + geom_histogram(bins =20)
-
-a1_set %>% ggplot(aes(x = GrLivArea, fill = Neighborhood)) + geom_histogram(bins =20)
 ```
@@
 #put the plots here
-plot(fit_transform)
 ```
 
-We find that the log-log transform has significantly reduced our residuals and given us a much better fit for the linear regression model, represented by bolstering our R\^2 compared to the previous non-transformed model.
+We find that the log-log transform has significantly reduced our residuals and given us a much better fit for the linear regression model, represented by bolstering our R^2 compared to the previous non-transformed model.
 We can see from the residual plots from the transformed fit that there are a few significantly high leverage/low residual points, and one out outlying point with a very high residual and leverage statistic.
@@
 
-For the second analysis in this project, we were tasked to generate 4 models using variations of parameters selected by Forward Selection, Backwards Elimination, Stepwise Selection, and a personalized approach.
-Using these paramters, we can generate Adjusted R\^2 values, CV Press statistics, and finally submit our model to the Kaggle website to obtain a "Kaggle Score" for each model.
+For the second analysis in this project, we have been tasked to build a predictive model that predicts the salary of houses provided the parameters of the dataset.
+The scope of this prediction is more general than the previous analysis question, focusing on the entire state of Iowa.
+Ultimately, the goal of these prediction is to compete against a known set on the website \textit{Kaggle} to receive a Kaggle score, demonstrating how accurate our prediction are.
+
+\subsection{Model Selection and Generation}
+
+Although we will be generating linear models for this analysis, the parameters for the model will be selected by a variety of selection methods, including, \textbf{forward selection, backwards elimination, and stepwise selection}.
+We will also be testing a set for which we select our own parameters to see how competitive we can get.
+
+To generate the models, we must take an approach to limit the multicollinearity of the dataset, otherwise the selection models will not work.
+To do this, we can create a correlation plot of all the numeric values within the dataset, and visualize which values are highly correlated.
 
 ```{r}
-plot(t1fit)
+transformed_numeric = numeric_housing
+selected = subset(transformed_numeric, select = -c(LotFrontage, MasVnrArea, GarageYrBlt))
+corrplot(cor(selected), tl.cex = 0.5)
 ```
+From this plot, we can eyeball the selection of highly correlated values, including \textit{"OverallQual, TotRmsAbvGrd, GarageCars, TotalBsmtSF, X1stFlrSF, X2ndFlrSF, FullBath"}.
+By removing these variables from the dataset, we reduce the colinearity of the set and allow for a better feature selection process.
 
-To improve the quality of our model, we decided to remove outliers as analaysis shows marginal improvements to R\^2 and marginal deterioration to the Press Statistic. We notice the following outliers:
+Running an initial backward selection model, we generate a series of residual plots that we can see below:
 
--   Excessively Expensive \> 700k SalePrice: ID #692 & \# 1183
+From the residual plots, we can see that due to the cloud-like random scattering of residuals, we've roughly explained the variations within the dataset with our model, this additionaly shows that there is no glaring breaks in variance.
+From the same plots, we can see that there is not sufficient evidence for any deviations from normality, seen in the QQ plots.We can additionalyly look at the VIFs for each model to numerically confirm that multicollinearity has been accounted for, with all numerical values falling below 3.
 
--   Excessively Large \> 100k sq ft.: ID #314, #226, #256, #707
+Results Table:
 
-Next, we removed the following highly correlated variables to reduce multicollinearity: LotFrontage, MasVnrArea, GarageYrBlt, OverallQual, TotRmsAbvGrd, GarageCars, TotalBsmtSF, X1stFlrSF, X2ndFlrSF, FullBath.
-In the correlation matrix, we can see which plots are correlated.
-After the elimination of the variables mentioned, we see more fairly spare correlated variables.
-
-```{r}
-corrplot(cor(t1))
-```
-
-Stepwise Selection
-
-Regression model:
-
-Mean(SalePrice) = b0 + b1(OverallQual) + b2(OverallCond) + b3(YearBuilt) + b4(
-
-## Model Results
-
-| Model                | Adjusted R\^2 | RMSE      | CVPress  |
-|----------------------|---------------|-----------|----------|
-| Forward Selection    | 0.8333        | 0.1620974 | 43.77074 |
-| Backward Elimination | 0.8333        | 0.1620974 | 43.77074 |
-| Stepwise Selection   | 0.8333        | 0.1620974 | 43.77074 |
-
-The rudimentary approach of numeric/reduced linearity set receives a Kaggle score of 0.20141.
-While is is interesting and good given the novel approach of the selection model, it's troubling to see that all 3 models returned the exact same Kaggle score, down to the last decimal.
-This may indicate that the models are adding/subtracting parameters to result in the exact same parameter list each time.
-This should be further investigated.
+\begin{center}
+\begin{tabular}{ |c|c|c|c| } 
+ \hline
+ Predictive Models & Adjusted R2 & CV PRESS & Kaggle Score \\ 
+ \hline
+ Forward & 0.8805 & 28.09 & 0.20061 \\
+ \hline
+ Backward & 0.8812 & 28.12 & 0.20061 \\
+ \hline
+ Stepwise & 0.8805 & 28.22 & 0.1814 \\
+ \hline
+ Custom & 
+\end{tabular}
+\end{center}
 
@@
 
-```{r echo = TRUE, results = 'hide', fig.show= 'hide'}
+```{r echo = TRUE, results = 'hide', fig.show= 'hide', warning=FALSE}
 
@@
 model1 <- train(SalePrice ~ GrLivArea + Neighborhood + GrLivArea*Neighborhood, data = a1_set, method = "lm", trControl = train.control1)
-CVPress(model1$model)# doesn't work atm
+#CVPress(model1$model) # doesn't work atm
 

### 2022-12-12 rough_analysis.Rmd
Add RShiny App Files
updates to analysis 2 and selection models

--- 2022-12-12 rough_analysis.Rmd
@@
 t1 = subset(transformed_numeric, select = -c(LotFrontage, MasVnrArea, GarageYrBlt, OverallQual, TotRmsAbvGrd, GarageCars, TotalBsmtSF, X1stFlrSF, X2ndFlrSF, FullBath ))
+
+t1 = t1[-c(524,1299),] #removing outliers -524, 1299 for outlying lot area
+
 #removal of largely correlated values to reduce multicollinearity (VIF /approx 1) and actually allow back-elimination to run,
@@
 backt1 = ols_step_backward_p(t1fit, prem = 0.05, details = FALSE)
-forwardt1 = ols_step_forward_p(t1fit, penter = 0.05, details = FALSE)               #the p-values for these should be fiddled with, 
-stepwiset1 = ols_step_both_p(t1fit, pent = 0.05, prem =0.05, details = FALSE)
+forwardt1 = ols_step_forward_p(t1fit, penter = 0.1, details = FALSE)               #the p-values for these should be fiddled with, 
+stepwiset1 = ols_step_both_p(t1fit, pent = 0.05, prem =0.01, details = FALSE)
 

### 2022-12-12 article.Rmd
updated final render of PDF + images

@@
 title: "Stats Project 2"
-author: Abhay Sharma | AbhaySh4r.github.io
+author: 
+  - Abhay Sharma | AbhaySh4r.github.io
+  - Carolina Craus | carolinacraus.github.io
 output:
-  pdf_document: default
+  pdf_document:
+    extra_dependencies: ['graphicx']
   html_notebook: default
@@
 ```
+\graphicspath{ {./images/} }
 
 \tableofcontents
+
+\\
+
+\textbf{Rshiny APP: https://carolinacraus.shinyapps.io/HousingApp/}
 
@@
 For this project, we are provided a housing data set from the website Kaggle that contains a large collection of parameters that are likely to be correlated with the Sale Price of their respective houses.
-Within this data set we find 79 parameters, some of which must ultimately be used to build a predictive model to extrapolate housing prices given a certain set of these parameters.
+This dataset was built and provided by Century 21 Ames.
+Within this data set we find 81 parameters and 1460 rows, some of which must ultimately be used to build a predictive model to extrapolate housing prices given a certain set of these parameters.
+Key variables to take note are \textit{GrLIvArea} which is defined as \textit{Above ground living area}; \textit{Neighborhood}, which is the region that each house is from, and \textit{SalePrice}, which is the price that the house was sold for.
 
@@
 \subsection{Model Generation and Analysis}
-To generate an initial model, we will look at a rudimentary approach to linear regression to see what our data does;
+To generate an initial model, we will look at a rudimentary approach to linear regression to see what our data does. Generating this model, seen in the Appendix results in the following residual plot.
 
-```{r echo = TRUE, results = 'hide', warning=FALSE}
-housing = read.csv(file = "train.csv")
-numeric_housing = housing %>% select_if(is.numeric)
-a1_set = housing %>% select(SalePrice, Neighborhood, GrLivArea) %>% filter( Neighborhood == c("NAmes", "Edwards", "BrkSide"))
-fit <- lm(SalePrice ~ GrLivArea + Neighborhood + GrLivArea*Neighborhood, data = a1_set)
-summary(fit)
-#plot(fit)
-#plot(a1_set$SalePrice, a1_set$GrLivArea)
-
-#put the plots here
+```{r, echo=FALSE,fig.cap="Residuals for standard linear model"}
+knitr::include_graphics("./images/residuals_fit.png")
 ```
@@
 
-```{r echo = TRUE, results = 'hide'}
-fit_transform <- lm(log(SalePrice) ~ log(GrLivArea) + Neighborhood + log(GrLivArea)*Neighborhood, data = a1_set)
-summary(fit_transform)
-confint(fit_transform)
-#plot(log(a1_set$GrLivArea), log(a1_set$SalePrice))
-#plot(fit_transform)
-
-#put the plots here
+```{r, echo=FALSE,fig.cap="Residuals for transformed linear model"}
+knitr::include_graphics("./images/residuals_fit_transform_image.png")
 ```
@@
 
-[picture of R table]
+```{r, echo=FALSE,fig.cap="Output Paramters of Model Summary", out.width= "60%",fig.align='center'}
+knitr::include_graphics("./images/transform_paramters.png")
+```
 
@@
 
-```{r}
-transformed_numeric = numeric_housing
-selected = subset(transformed_numeric, select = -c(LotFrontage, MasVnrArea, GarageYrBlt))
-corrplot(cor(selected), tl.cex = 0.5)
+```{r, echo=FALSE,fig.cap="Correlation Matrix"}
+knitr::include_graphics("./images/numerical_correlation.png")
 ```
+
 From this plot, we can eyeball the selection of highly correlated values, including \textit{"OverallQual, TotRmsAbvGrd, GarageCars, TotalBsmtSF, X1stFlrSF, X2ndFlrSF, FullBath"}.
@@
 
+```{r, echo=FALSE,fig.cap="Residuals for backwards elimination model"}
+knitr::include_graphics("./images/residuals_backt1.png")
+```
+
 From the residual plots, we can see that due to the cloud-like random scattering of residuals, we've roughly explained the variations within the dataset with our model, this additionaly shows that there is no glaring breaks in variance.
@@
 
-Results Table:
+\subsection{Comparing Competing Models}
+
+The following is the Results Table, from which we can analyze core components of each selection model:
 
@@
  \hline
- Custom & 
+ Custom & 0.846 & 38.28 & 0.20293 \\
+ \hline
 \end{tabular}
 \end{center}
+
+For the models, we restricted paramter selection to only numeric and limited coorelated parameters.
+This initial approach led to competitive and interesting Kaggle scores.
+However, our custom approach intended on adding categorical variables to identify more interactions.
+Our initial approach seemed to lower our Kaggle score, so we didn't pursue that specific model more than what we had.
+
+Ideally we believe that a proper execution of adding in categorical variables to the selection pool should result in a decreased Kaggle Score.
+
+\subsection{Conclusion}
+
+  For Analysis 2, we were required to create 4 prediction models that, that atleast somewhat accurately predicted the sale price of houses sold within the Ames Iowa region.
+To use the data, we had to address issues of outliers and multicollinearity within the dataset, and narrowed our functional dataset to only numerical values.
+Using forwards selection, backwards elimination, stepwise selection, and our own custom selected parameter approach, we generated mildly competitive prediction results with Kaggle scores of \textbf{0.20061, 0.20061, 0.1814, 0.20293}, respectively.
+For the custom approach, although we did not see large gains, we believe that the approach of introducing categorical variables can be successful and should be studied more, for a more thorough model.
+
+\newpage
 
@@
 
+## Custom Model: # Change categorical values to numeric
+housing2 = housing
+housing2$Neighborhood <- as.numeric(factor(housing2$Neighborhood,
+                                                        levels = c("Blmngtn", "Blueste", "BrDale"),
+                                                        labels = c(2,1,0), ordered = TRUE))
+housing2$LotConfig <- as.numeric(factor(housing2$LotConfig,
+                                                        levels = c("Inside", "Corner", "CulDSac", "FR2", "FR3"),
+                                                        labels = c(4,3,2,1,0), ordered = TRUE))
+housing2$ExterQual <- as.numeric(factor(housing2$ExterQual,
+                                                        levels = c("Ex", "Gd", "TA", "Fa", "Po"),
+                                                        labels = c(4, 3, 2,1,0), ordered = TRUE))
+housing2$BsmtQual <- as.numeric(factor(housing2$BsmtQual,
+                                                        levels = c("Ex", "Gd", "TA", "Fa", "Po"),
+                                                        labels = c(4, 3, 2,1,0), ordered = TRUE))
+
+normal_housing = housing 
+normal_set = normal_housing %>% select(SaleCondition) %>% filter( SaleCondition == c("Normal"))
+normal_housing = normal_housing %>% select_if(is.numeric)
+normal_housing$SalePrice = log(normal_housing$SalePrice)
+normal_housing$GrLivArea = log(normal_housing$GrLivArea)
+
+t2 = subset(normal_housing, select = -c(LotFrontage, MasVnrArea, GarageYrBlt, OverallQual, TotRmsAbvGrd, GarageCars, TotalBsmtSF, X1stFlrSF, X2ndFlrSF, FullBath )) 
+#removal of largely correlated values to reduce multicollinearity (VIF /approx 1) and actually allow back-elimination to run,
+#it wasn't running without a ton of errors without this. 
+corrplot(cor(t2)) #visualize correlation to identify which plots are correlated. After elimiation, it should be fairly sparsely correlated. 
+t2fit = lm(SalePrice ~. , data = t2)
+backt2 = ols_step_backward_p(t2fit, prem = 0.05, details = FALSE)
+forwardt2 = ols_step_forward_p(t2fit, penter = 0.05, details = FALSE)               #the p-values for these should be fiddled with, 
+stepwiset2 = ols_step_both_p(t2fit, pent = 0.05, prem =0.01, details = FALSE)
+forwardt2
+backt2
+stepwiset2
+#mystery4thsetWIP
+#---------------------------------Summary Stats of the produced RL sets
+summary(backt2$model)
+vif(backt2$model)
+ModelRMSE(backt2$model$residuals)
+CVPress(backt2$model)
+#---------------------------------
+summary(forwardt2$model)
+vif(forwardt2$model)
+ModelRMSE(forwardt2$model$residuals)
+CVPress(forwardt2$model)
+#---------------------------------
+summary(stepwiset2$model)
+vif(stepwiset2$model)
+ModelRMSE(stepwiset2$model$residuals)
+CVPress(stepwiset2$model)
 ```

### 2022-12-12 article.Rmd
added final ggplot to visualize model

@@
 
-```{r, echo=FALSE,fig.cap="Output Paramters of Model Summary", out.width= "60%",fig.align='center'}
+```{r, echo=FALSE,fig.cap="Output Parameters of Model Summary", out.width= "60%",fig.align='center'}
 knitr::include_graphics("./images/transform_paramters.png")
@@
 Although the Edwards housing region has marginally varying statistics to the Brookside region, they are not statistically significant enough to indicate any explain any variation by themselves, and thus housing prices should follow the same trend.
+We can visualize these by plotting the linear model of the data and visually confirm that the changes in slope and intercept are indeed represented in the model.
+
+```{r, echo=FALSE,fig.cap="Plot of LR model", out.width= "40%",fig.align='center'}
+knitr::include_graphics("./images/updatedlinearimage.png")
+```
 
@@
 
-```{r, echo=FALSE,fig.cap="Correlation Matrix"}
+```{r, echo=FALSE,fig.cap="Correlation Matrix", out.width="70%", fig.align='center'}
 knitr::include_graphics("./images/numerical_correlation.png")
@@
 
-```{r, echo=FALSE,fig.cap="Residuals for backwards elimination model"}
+```{r, echo=FALSE,fig.cap="Residuals for backwards elimination model", out.width= "60%", fig.align="center"}
 knitr::include_graphics("./images/residuals_backt1.png")
